Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment in $V$ that crosses $r$.
}
Define $r' = [x_1, x_2] \times [y_1, y_2]$, where $x_1$ (resp., $x_2$) is x-coordinate of $v_1$ (resp., $v_2$), and $y_1$ (resp., $y_2$) is y-coordinate of $h_1$ (resp., $h_2$). We say that $r'$ is the {\em trimmed rectangle} of $r$, and conversely, $r$ is the {\em full rectangle} of $r'$. Note that $r'$ exists if and only if $r$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$.

@@

Construct
\myeqn{
    R_i' &=& \set{r' \mid r \in R_i \text{ and its trimmed rectangle $r'$ exists}}. \nn
}
Computing the ``segment $h_1$'' for each $r \in R_1$ is an instance of Problem $\mathscr{D}$ (the find-lowest version). By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1', R_2', ..., R_{k-2}'$ can be produced in $O(n \log n)$ total time.

>>>>

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment in $V$ that crosses $r$.
}
Define $r' = [x_1, x_2] \times [y_1, y_2]$, where $x_1$ (resp., $x_2$) is x-coordinate of $v_1$ (resp., $v_2$), and $y_1$ (resp., $y_2$) is y-coordinate of $h_1$ (resp., $h_2$). We say that $r'$ is the {\em trimmed rectangle} of $r$, and conversely, $r$ is the {\em full rectangle} of $r'$. Note that $r'$ exists if and only if $r$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$.

%Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$.

@@

Construct
\myeqn{
    R_i' &=& \set{r' \mid r \in R_i \text{ and its trimmed rectangle $r'$ exists}}. \nn
}
Computing the ``segment $h_1$'' for each $r \in R_i$ is an instance of Problem $\mathscr{D}$ (the find-lowest version). By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r \in R_i$. It thus follows from Section~\ref{sec:bricks} that $R_1', R_2', ..., R_{k-2}'$ can be produced in $O(n \log n)$ total time.
